---
title: "Mapping Species Occurrences"
output: pdf_document
---

## Mapping Species Occurrences

Your Name(s) 
Group Name 
Mapping Species Occurrences 
Feburary 15th 

There are two big goals of today's R Notebook:

* Practicing the integration of GitHub into your workflow. 
* Diving deeper into using R to map species distrubution.  

### GitHub integration

* get token. 
* setup & run github.R. (I think everyone can do this simultaneously, though maybe they should wait)
* add github integration to Slack. 

Workflow:
* write some code
* commit. 
* push.
* pull (if you need to get the latest code)
* Use Slack to communicate! (e.g. "ok, I just pushed to github, go ahead and pull)


Practice:

Group member 1:
* write code in the code chunk below to query milkweed species from GBIF
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}



```


Group member 2:
* write code in the code chunk below to query milkweed species from GBIF
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}



```


Group member 3:
* write code in the code chunk below to query milkweed species from GBIF
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}



```

Group member 4 (if applicable):
* write code in the code chunk below to query milkweed species from GBIF
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}



```



### Mapping




