---
title: "Mapping Species Occurrences"
output: pdf_document
---

## Mapping Species Occurrences

Your Name(s) 
Group Name 
Mapping Species Occurrences 
Feburary 15th 

There are two big goals of today's R Notebook:

* Practicing the integration of GitHub into your workflow. 
* Diving deeper into using R to map species distribution.  


First, install and load packages:

```{r}
# install packages
install.packages("spocc")
install.packages("tidyverse")
install.packages("maptools")


install.packages("dismo")

install.packages("rgdal")
install.packages("raster")
install.packages("sp")
install.packages("sf")


```


```{r}
# load packages:

library("spocc")
library("sp")
library("raster")
library("maptools")
library("rgdal")
library("dismo")
library("sf")


```




### GitHub integration

* get token. 
* setup & run github.R. (I think everyone can do this simultaneously, though maybe they should wait)
* add github integration to Slack. 

Workflow:
* write some code
* commit. 
* push.
* pull (if you need to get the latest pushed code from github)
* Use Slack to communicate! (e.g. "ok, I just pushed to github, go ahead and pull)


Practice:

Group member 1:
* write code in the code chunk below to query milkweed species from GBIF
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}



```


Group member 2:
* write code in the code chunk below to query milkweed species from GBIF
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}



```


Group member 3:
* write code in the code chunk below to query milkweed species from GBIF
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}



```

Group member 4 (if applicable):
* write code in the code chunk below to query milkweed species from GBIF
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}



```


### Data cleaning


Just like in the last exercise, it's important to look for errors in the data.
Check here for a refresher: https://github.com/BiodiversityDataScienceCorp/more-querying-gbif-data/blob/main/more-querying-gbif.Rmd

Group Member 1:

Check for and filter out any data in which occurrenceStatus=="Absent"
* write code below
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}




```


Group Member 2:

Check for and filter out any occurrences in which individualCount==0
* write code below
* Commit
* Push
* Tell your groupmates to pull in Slack

```{r}




```


Group Member 3:

Check for obvious errors in lat/long. Remove those points if necessary.
* write code below
* Commit
* Push
* Tell your groupmates to pull in Slack



Group Member 4 (or 1):

Reduce data columns, and save to a CSV file
* write code below
* Commit
* Push
* Tell your groupmates to pull in Slack



### Mapping

We did a little bit of mapping in the last assignment, when we were checking for erroneous points. Now let's try to make a more fine-tuned map of species occurrences, with the goal of creating ans image you could use in your final report.

There are numerous ways to create a map in R. We're going to look at one method here, but don't feel restricted if you want to try a different technique. Searching in Google is an effective way to learn about alternatives.

Let's look at an example using the Goldfinch data.

First we want to load the data set:

```{r}
goldfinches<-read_csv("goldfinchOr.csv")
goldfinches
```


Now let's determine the minimum and maximum latitudes and longitudes of the data set. This will help us define where to focus the map. We want our boundaries to be slightly larger than all points contained:

```{r}

# ceiling returns the smallest integer that is greater than or equal to a value
# max gives the largest value of the column data
# so if the highest value in goldfinches$latitude is 46.5, then its ceiling is 47

max.lat <- ceiling(max(goldfinches$latitude))

# floor and min work similarly (but opposite)
# if the lowest value of goldfinches$latitude is 43.84, then its floor is 43

min.lat <- floor(min(goldfinches$latitude))

# run same calculations for longitude

max.lon <- ceiling(max(goldfinches$longitude))
min.lon <- floor(min(goldfinches$longitude))



```


Now these values are ready to use in the map code. 

In the sequence below, I'll first indicate that I want to save the output as a jpg. Then 


```{r}
# indicates that I want to save the next output as "or.jpg"
jpeg(file="or.jpg")

# this loads spatial polygons
data(wrld_simpl)

# Plot the base map
plot(wrld_simpl, 
     xlim = c(min.lon, max.lon), # sets upper/lower x
     ylim = c(min.lat, max.lat), # sets upper/lower y
     axes = TRUE, 
     col = "grey95",
     main="Goldfinch species occurrences in Oregon, 2020",  # a title
     sub="an informative caption" # a caption
     )

# Add the points for individual observation
points(x = goldfinches$longitude, 
       y = goldfinches$latitude, 
       col = "blue", 
       pch = 20, 
       cex = 0.75)
# And draw a little box around the graph
box()

# indicates I'm done with plotting and saving to jpg
dev.off()
```


Select a group member to create a map of your milkweed occurrence data. Follow the example above: first determine your min/max lat/lon, and then generate the map code. Save this as a jpg file. Then commit, and push to Github (and have your group members pull).

```{r}





```


Download your map jpg, and submit it to the assignment 5 folder.
